A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-08 survey.tex
Authors names

\author{FirstName~LastName,~\IEEEmembership{Member,~IEEE,}
        Jim~Raynor,~\IEEEmembership{Fellow,~RR,}
        and~Sarah~Kerrigan,~\IEEEmembership{Life~Fellow,~ZS}% <-this % stops a space
\thanks{FirstName~LastName is with the Department of Names
GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
\thanks{J. Raynor and S. Kerrigane are with the Romeo\&Juliet Inc.}% <-this % stops a space
\thanks{Manuscript received April 19, 2499; revised January 11, 2500.}}

>>>>

% \author{FirstName~LastName,~\IEEEmembership{Member,~IEEE,}
%         Jim~Raynor,~\IEEEmembership{Fellow,~RR,}
%         and~Sarah~Kerrigan,~\IEEEmembership{Life~Fellow,~ZS}% <-this % stops a space
% \thanks{FirstName~LastName is with the Department of Names
% GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
% \thanks{J. Raynor and S. Kerrigane are with the Romeo\&Juliet Inc.}% <-this % stops a space
% \thanks{Manuscript received April 19, 2499; revised January 11, 2500.}}

\author{Santiago~Onta\~{n}\'{o}n,
        Gabriel~Synnaeve,
        Alberto~Uriarte,
        Florian~Richoux,
        Dave~Churchill,
        Mike~Preuss
}
